Spec2Fab: A High-Fidelity Mapping from Specification to Fabrication

### 2012-10-08 paper.tex
in each experiment , what generators to use

\section{Built-in Components}
We provide a built-in library that handles common tasks such as assigning texture,
simulating deformation, and optimizing for a stacking.
\subsection{Generator}
Generator uses a reduced representation
of material assignments.
Each generator is defined over a domain in the input shape.
We provide a few basic generators and a composition operator.
Let the input shape be over a domain $\Omega$.
The composition of two generators $G_2\circ G_1$ is implemented by
first letting $G_1$ reduce over a domain $\Omega_1$ and
then letting $G_2$ reduce $\Omega_2 = \Omega-\Omega_1$.
An example is shown in Figure~\ref{fig:genCompose}
\begin{figure}[h]
\includegraphics[scale=0.2]{figure/genCompose.png}
\caption{Composition of two generators. $G_1$ is a fine-grained
surface voxelization and $G_2$ is a very coarse inner
grid.}
\label{fig:genCompose}
\end{figure}
\begin{enumerate}
\item A generator that uses a uniform grids with homogeneous
material in each grid cell. (A foam structure is treated as one homogeneous material).
\item A generator that decomposes a mesh into columns of stackings where each
column can be addressed separately by Generator::chooseSection.
This is useful for problems where local changes don't global effects such as
matching texture, matching mechanical properties of each column.
\item A polynomial spline representation for modifying the surface mesh.
\item A polynomial spline for height field of internal material layers (does not modify
surface mesh).
\end{enumerate}

\subsection{Simulator}
\begin{enumerate}
\item Physics simulator with FEM, rigid body simulation
and simple collision resolution.
\item nVidia optiX to do photon mapping for caustics. Maybe also BRDF and shadows.
We need to look at its speed.
\item local computations such as reflectance and local mechanical properties given a stacking.
\end{enumerate}

@@

\section{Experiments}
\subsection{Print Material Characterization and Measurement}

\subsection{Subsurface Scattering, Deformation and Mass}
Combining previous work on replicating
subsurface scattering and deformation behavior, 
we produced
material with a particular
look and deformation properties as shown in Figure~\ref{fig:deform}.
We als considered one additional property:mass. In this example, we
tried to make the material as light as possible.
\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
	\centering
 	\includegraphics[width=\textwidth]{figure/slab_origin.png}
   	\caption{}
    \label{fig:deformPhoto}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.3\textwidth}
    \centering
  	\includegraphics[width=\textwidth]{figure/slab_deform.png}
    \caption{}
    \label{fig:deformPrint}
\end{subfigure}
\caption{Simutaneously matching appearance and deformation. 
(a)Original slab of a particular looking. (b)printed slab 
with the same looking and desired deformation.}
\label{fig:deform}
\end{figure}

@@

\section{Caustics for a Mesh}
We demonstrate how to produce a 3D model with specific caustic shape under a particular lighting,
similar to \cite{Finckh:2010}. The difference is that we optimize on an arbitrary 3D model,
and we use a generic rendering package (NVidia optiX). Our algorithm took 6 hours to finish
with $4000$ spline control points for the model and $600\times 600$ resolution for the caustic image. A 
picture of our printed result under desired lighting is shown in Figure~\ref{fig:caustic}.

@@

We expand gamut of printable colors by stacking translucent materials. We then applied
dithering with our expanded colors.
Results are shown in Figure~\ref{fig:texture}
\subsection{New Examples for Mechanical Properties}
Ball bounce to certain height.

@@

A loaded die as shown in Figure~\ref{fig:die}. This example is interesting because
a local change will have some global effect.
\begin{figure}
	\centering
 	\includegraphics[width=0.25\textwidth]{figure/die.png}
\caption{A printed loaded die}
\label{fig:die}
\end{figure}
It has a certain probability to land on "1".
A table of probability distribution of landing on each side
is shown in Table~\ref{tab:dice}.

>>>>

\section{Built-in Components}
We provide a built-in library that handles common tasks such as assigning texture,
simulating deformation, and optimizing for a stacking.
\subsection{Generator}
Generator uses a reduced representation
of material assignments.
Each generator is defined over a domain in the input shape.
We provide a few basic generators and a composition operator.
Let the input shape be over a domain $\Omega$.
The composition of two generators $G_2\circ G_1$ is implemented by
first letting $G_1$ reduce over a domain $\Omega_1$ and
then letting $G_2$ reduce $\Omega_2 = \Omega-\Omega_1$.
An example is shown in Figure~\ref{fig:genCompose}
\begin{figure}[h]
\includegraphics[scale=0.2]{figure/genCompose.png}
\caption{Composition of two generators. $G_1$ is a fine-grained
surface voxelization and $G_2$ is a very coarse inner
grid.}
\label{fig:genCompose}
\end{figure}

We will provide the following generators.
\begin{enumerate}
\item A generator that uses a uniform grids with homogeneous
material in each grid cell. (A foam structure is treated as one homogeneous material).
\item A generator that decomposes a mesh into columns of stackings.
\item A polynomial spline for outline of a material.
\end{enumerate}
We use composition of the above basic generators to make the examples in 
the result section.
\subsection{Simulator}
\begin{enumerate}
\item Physics simulator with FEM, rigid body simulation
and simple collision resolution.
\item nVidia optiX to do photon mapping for caustics. Maybe also BRDF and shadows.
We need to look at its speed.
\item local computations such as reflectance and local mechanical properties given a stacking.
\end{enumerate}

@@

\section{Experiments}
We used various generators in our experiments.
\subsection{Print Material Characterization and Measurement}
\subsection{Subsurface Scattering, Deformation and Mass}
Combining previous work on replicating
subsurface scattering and deformation behavior, 
we produced
material with a particular
look and deformation properties as shown in Figure~\ref{fig:deform}.
We als considered one additional property:mass. 
In this example, we
tried to make the material as light as possible.

We tried different combinations of generators in this experiment.
We compared the performance of these different generator
in terms of run-time and error.
\begin{enumerate}
\item Spline for top layer, fine-grained voxelization for mid layer
and a coarse grid for bottom layer.
\item Voxels for top layer, splines for middle layer and a coarse
bottom layer.
\item Find-grained voxels for top layer and coarse grid for bottom layer.
\end{enumerate}

\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
	\centering
 	\includegraphics[width=\textwidth]{figure/slab_origin.png}
   	\caption{}
    \label{fig:deformPhoto}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.3\textwidth}
    \centering
  	\includegraphics[width=\textwidth]{figure/slab_deform.png}
    \caption{}
    \label{fig:deformPrint}
\end{subfigure}
\caption{Simutaneously matching appearance and deformation. 
(a)Original slab of a particular looking. (b)printed slab 
with the same looking and desired deformation.}
\label{fig:deform}
\end{figure}

@@

\subsection{Caustics for a Mesh}
We demonstrate how to produce a 3D model with specific caustic shape under a particular lighting,
similar to \cite{Finckh:2010}. The difference is that we optimize on an arbitrary 3D model,
and we use a generic rendering package (NVidia optiX). 
We represented the surface with a spline surface.
Our algorithm took 6 hours to finish
with $4000$ spline control points for the model and $600\times 600$ resolution for the caustic image. A 
picture of our printed result under desired lighting is shown in Figure~\ref{fig:caustic}.

@@

When printing texture, only the outer layer matters. We used 
a composition of two generators: a very high resolution grid
for the outer layer and a uniform material for the inside.

We expand the set of printable colors by stacking translucent materials. We then applied
dithering with our expanded colors.
Results are shown in Figure~\ref{fig:texture}
\subsection{New Examples for Mechanical Properties}
Ball bounce to certain height. We used a higher resolution
grid for the out layer and very low resolution
for the inner mesh.

@@

A loaded die as shown in Figure~\ref{fig:die}. This example is interesting because
a local change will have some global effect.
We used very high resolution grid for the surface to match texture
of a die. The inner lay has only $3\times 3$ resolution.
\begin{figure}
	\centering
 	\includegraphics[width=0.25\textwidth]{figure/die.png}
\caption{A printed loaded die}
\label{fig:die}
\end{figure}
It has a certain probability to land on "1".
A table of probability distribution of landing on each side
is shown in Table~\ref{tab:dice}.
